---
title: "FitBit Prediction"
author: "D Lynch"
date: "27 September 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Your submission for the Peer Review portion should consist of a link to a Github repo with your R markdown and compiled HTML file describing your analysis. Please constrain the text of the writeup to < 2000 words and the number of figures to be less than 5. It will make it easier for the graders if you submit a repo with a gh-pages branch so the HTML page can be viewed online (and you always want to make it easy on graders :-). chunk like this:

```{r}

```

```{r}

```

```{r}

```


```{r}

```

```{r}

```

```{r}

```


```{r}

```

```{r}

```

```{r}

```


```{r}

```

```{r}

```

```{r}

```


```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```


```{r}

```

```{r}

```

```{r}

```


```{r}

```

```{r}

```

```{r}

```


```{r}

```

```{r}

```

```{r}

```


```{r}

```

```{r}

```

```{r}

```



